\chapter{Work In Progress}
Our ongoing tasks are listed below:
\begin{enumerate}[label=\arabic*.]
    \item \textbf{Parameter Tuning and Optimization:} \\
    After training our model, the accuracy of the model came quite low. So, we are currently focusing on tuning the parameters of our training process to achieve better results and . Additionally, our aim is to optimize our processes to expedite result prediction. This involves a thorough examination of our existing methodologies and fine-tuning them for improved performance.
    
    \item \textbf{Dataset Combination:} \\
    Our datasets have been divided into sections of 10,000 each. We are in the process of combining these datasets to provide more accurate prediction accuracy. This step is crucial as it ensures that our model is trained on a comprehensive dataset, thereby enhancing its predictive capabilities.
    
    \item \textbf{Code Integration and Website Development:} \\
    The code we are using is predominantly in MATLAB. However, we are currently in the process of deciding whether to integrate this code with the website side of our project. This decision will impact the user interface and functionality of our project therefore, we are desiginig our website for better user interface.
    
    \item \textbf{Ongoing Collaboration and Communication:} \\
    We continue to engage in weekly discussions with team members to provide updates and share progress. Additionally, frequent meetings with our supervisor are being held to ensure that we are on the right track and to explore any potential areas for improvement. This collaborative approach is essential for achieving optimum results and refining our working methods.

    
    \item \textbf{Feature Extraction Exploration:} \
    To further improve our model's predictive capabilities, we are actively exploring and implementing available  feature extraction techniques. This involves identifying and selecting more relevant features from our data, aiming to enhance the discriminative power of the model which helps us in increasing for the predictive accuracy.


\end{enumerate}